Stack Safety as a Security Property

### 2020-06-22 main.tex
Skipping broken citation for now

But what {\em is} stack safety? A formal definition of stack safety is
lacking from the literature, with the notion only being defined
negatively: through examples of stack unsafety. Two classical examples
of stack unsafety appear in Figure~\ref{fig:stackunsafety}.
\leo{Goal: on the left, a bad read; on the right, a bad write.}
\leo{Do we also need an example of ROP/control flow for the new part?}

@@

We begin by giving some background in Section~\ref{sec:prelim}.
Our contributions are:
\begin{itemize}
\item A formal property capturing the local state encaptulation
  notion of stack safety.
\item Evidence that this property is strong enough to capture the folk
intuition: we show that the stack
  unsafe examples from the literature also fail our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism \leo{And it
    says yes on a substantial body of code}
\item A (inductive? step-by-step/stepwise) variant of this property
  tuned for testing/verification together with a proof that it implies
  the original property.  We test the whole thing with a cool
  framework.
\item A lazy version of the property that allows for more efficient/dynamic enforcement.
  Maybe testing.
\item An extension to this formal property that enforces well-bracketed
  control flow and an accompanying policy.
\end{itemize}
Finally, in Section~\ref{sec:relwork} we discuss related work and
sketch directions for future work in Section~\ref{sec:future}.

@@

    While these ideas are here presented in a stack-centric style, they could
    be extended to heap safety in a system extended with a heap. Heap safety,
    like stack safety, may be framed as a form of noninterference
    \cite{AzevedoDeAmorim17}. As in stack safety, the mapping from components
    to security labels would be dynamic, with any heap data unreachable from
    the stack frame in a given state treated as high confidentiality and high
    integrity. This would require updating the contour at each step.

@@

%% Bibliography
%\bibliography{bibfile}

>>>>

But what {\em is} stack safety? A formal definition of stack safety is
lacking from the literature, with the notion only being defined
negatively: through examples of stack unsafety. Two classical examples
of stack unsafety appear in Figure~\ref{fig:stackunsafety}.
\leo{Goal: on the left, a bad read; on the right, a bad write.}
\leo{Do we also need an example of ROP/control flow for the new part?}
\leo{Stack tokens introduce two properties: lse + wbcf, high level
  semantics, refinement to a machine with ``builtin'' ``by construction''
  (pretty weak :)) We make them formal and extensional}

@@

We begin by giving some background in Section~\ref{sec:prelim}.
Our contributions are:
\begin{itemize}
\item \leo{More? Extensional} formal characterizations of the intuitive concepts
  of local state encapsualtion \leo{ref} and well-bracketed control flow \leo{ref}.
  Evidence that this property is strong enough to capture the folk
  intuition: we show that the stack unsafe examples from the literature also fail
  our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism \leo{And it
    says yes on a substantial body of code}
  We then present a variation of the property + policy that is lazy,
  easier/more efficient to implement, and provably weaker.
\item A provably stronger (inductive? step-by-step/stepwise) variant
  of this property tuned for testing/verification.  We test the whole
  thing with a cool framework.
\end{itemize}
Finally, in Section~\ref{sec:relwork} we discuss related work and
sketch directions for future work in Section~\ref{sec:future}.

@@

    While these ideas are here presented in a stack-centric style, they could
    be extended to heap safety in a system extended with a heap. Heap safety,
    like stack safety, may be framed as a form of noninterference
    [cite Meaning of Memory Safety]. As in stack safety, the mapping from
    components to security labels would be dynamic, with any heap data
    unreachable from the stack frame in a given state treated as high
    confidentiality and high integrity. This would require updating the contour
    at each step.

@@

%% Bibliography
%\bibliography{bcp.bib}
